Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-10-26 manuscript/text_reuse.tex
added info on bill metadata

>>>>

This collection of bills is based on all bills that are available through the \url{openstates.org} API. Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted. The database contains the full bill text and the following additional metadata:
\begin{itemize}
    \item action_dates:
        \begin{itemize}
            \item first
            \item last
            \item passed lower
            \item passed upper
            \item signed
        \end{itemize}
    \item actions (a list of legislative actions. E.g. referred to a committee)
        \begin{itemize}
            \item actor
            \item date 
            \item related_entities 
            \item type
        \end{itemize}
    \item bill document first
    \item bill document last
    \item bill id
    \item bill title
    \item date created
    \item date introduced
    \item date signed
    \item date updated
    \item session
    \item short title
    \item state
    \item summary
    \item sunlight_id
    \item unique id
\end{itemize}
